%% =========================================================================
\section{Conclusion}
%% =========================================================================

This report examined the dynamic behaviour of
synchronous generators under three scenarios of increasing complexity through
MATLAB R2025b / Simscape Electrical simulation, verified against governing
equations from power systems theory.

\textbf{Exercise~1} established the two fundamental coupled control mechanisms
of a synchronous machine: the swing-equation/governor loop coupling active power
to frequency, and the Q-equation/AVR loop coupling reactive power to terminal
voltage. The \MVA{555} machine exhibited robust AVR action, recovering from a
severe \pu{0.82} voltage dip within 3--4 seconds, and governor-controlled
frequency settling at droop-governed steady-state values precisely as predicted
by \eqnref{eq:droop_calc_3s}.

\textbf{Exercise~2} demonstrated that the governor frequency setpoint is the
sole determinant of load sharing in parallel operation. An under-frequency
oncoming machine (Task~3) draws power from the system --- a hazardous motoring
condition that can overload the running generator. An over-frequency machine
(Task~4) assumes the majority of the system load --- the desired operational
outcome. In both cases, the system frequency settled at a droop-weighted
average of the two setpoints, confirming \eqnref{eq:combined_droop}.

\textbf{Exercise~3} revealed the fundamental distinction between finite and
infinite bus behaviour. Connected to an infinite bus, Generator~B loses all
ability to influence system frequency. Its active power is set by its governor
setpoint relative to the immovable grid frequency, resulting in a more severe
motoring condition in Task~5 and a clean power injection in Task~6. This models
the real-world scenario of a small generator connecting to a national grid ---
the grid's frequency is determined by millions of megawatts of inertia, and a
single machine has negligible influence on it.
